---
title: "Predicting Product Backorder -- Cluster then Predict Model"
output: html_document
date: "2023-02-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caTools)
library(caret)
library(psych)
library(flexclust)
library(dplyr)
library(e1071)
library(ROCR)
```

Load data
```{r}
train = read.csv("Competition_Train.csv")
test = read.csv("Competition_Test.csv")
str(train)
str(test)
```

Note: leave variables as int/ num for clustering. Change to factor variables before logistic regression.

Data Preprocessing
```{r}
# Remove target variable (went on back order) and SKU variable.
limitedTrain = train
limitedTrain$sku = NULL
limitedTrain$went_on_backorder = NULL 

limitedTest = test
limitedTest$sku = NULL

# Preprocess & normalise train & test data 
preproc = preProcess(limitedTrain)
normTrain = predict(preproc, limitedTrain)
normTest = predict(preproc, limitedTest)
summary(normTrain)
SD(normTrain, na.rm = TRUE)
```

--- K-MEANS CLUSTERING ---
```{r}
set.seed(1)
km = kmeans(normTrain, centers = 4)

km.kcca = as.kcca(km, normTrain)
clusterTrain = predict(km.kcca)          
clusterTest = predict(km.kcca, newdata = normTest)
```

--- LOGISTIC REGRESSION ---

Data preprocessing

# Test for multicollinearity 
cor(train)
# remove forecast 3 & 6 month
# remove sales 1, 3, 6 month
# remove perf 6 month avg 

# Drop columns with multicollinearity 
train_wo_mulcol = train %>% select(-c(forecast_3_month, forecast_6_month, sales_1_month, sales_3_month, sales_6_month, perf_6_month_avg))

# Check multicollinearity
cor(train_wo_mulcol)

# remove min_bank?
train_wo_mulcol = train_wo_mulcol %>% select(-min_bank)


CROSS VALIDATION

```{r}
# Convert to factor variables -- TRAIN SET
str(train) 
train$potential_issue = as.factor(train$potential_issue)
train[18:23] = lapply(train[18:23], as.factor) 
```


Prepare for Cross Validation 

"No" = did not go on back order
"Yes" = went on back order
```{r}
train$went_on_backorder = revalue(train$went_on_backorder, c("0"="No", "1"="Yes"))
str(train) 
```


Build Cross Validation Models 

```{r}
fitControl = trainControl(method = "cv", number = 10, classProbs = TRUE, summaryFunction = twoClassSummary)
```

```{r}
Train1 = subset(train, clusterTrain == 1)
Train2 = subset(train, clusterTrain == 2)
Train3 = subset(train, clusterTrain == 3)                   
Train4 = subset(train, clusterTrain == 4)
```

--- Model 1 (Train1) ---

```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + sales_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + ppap_risk + stop_auto_buy, data = Train1, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```
lowest forecast/ sales/ performance months
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_1_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + ppap_risk + stop_auto_buy, data = Train1, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

BEST MODEL1
rm sales var
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + ppap_risk + stop_auto_buy, data = Train1, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

add min_bank, remove corr variables
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + potential_issue + pieces_past_due + local_bo_qty + min_bank + deck_risk + ppap_risk + stop_auto_buy, data = Train1, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```
change around forecast/ sales/ performance months
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_9_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + ppap_risk + stop_auto_buy, data = Train1, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

--- Model 2 (Train2) ---

```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + sales_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + stop_auto_buy, data = Train2, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

BEST MODEL2
lowest forecast/ sales/ performance months
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_1_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + stop_auto_buy, data = Train2, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

rm forecast, perf vars
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + potential_issue + pieces_past_due + local_bo_qty + deck_risk + stop_auto_buy, data = Train2, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

--- Model 3 (Train3) ---
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + sales_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + oe_constraint + ppap_risk + stop_auto_buy + rev_stop, data = Train3, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

BEST MODEL3
lowest forecast/ sales/ performance months
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_1_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + oe_constraint + ppap_risk + stop_auto_buy + rev_stop, data = Train3, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

rm forecast var
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + sales_1_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + oe_constraint + ppap_risk + stop_auto_buy + rev_stop, data = Train3, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

--- Model 4 (Train4) ---

BEST MODEL4
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + sales_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + stop_auto_buy, data = Train4, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

lowest forecast/ sales/ performance months
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_1_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + stop_auto_buy, data = Train4, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

rm forecast, perf vars
```{r}
set.seed(1)
train(went_on_backorder ~ national_inv + lead_time + in_transit_qty + sales_9_month + potential_issue + pieces_past_due + local_bo_qty + deck_risk + stop_auto_buy, data = Train4, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

In Sample Testing

FINAL MODELS 1-4
```{r}
Model1 = glm(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + ppap_risk + stop_auto_buy, data = Train1, family = "binomial")
Model2 = glm(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_1_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + stop_auto_buy, data = Train2, family = "binomial")
Model3 = glm(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_3_month + sales_1_month + potential_issue + pieces_past_due + perf_6_month_avg + local_bo_qty + deck_risk + oe_constraint + ppap_risk + stop_auto_buy + rev_stop, data = Train3, family = "binomial")
Model4 = glm(went_on_backorder ~ national_inv + lead_time + in_transit_qty + forecast_9_month + sales_9_month + potential_issue + pieces_past_due + perf_12_month_avg + local_bo_qty + deck_risk + stop_auto_buy, data = Train4, family = "binomial")
```

```{r}
predictTrain1 = predict(Model1, type = "response")
predictTrain2 = predict(Model2, type = "response")
predictTrain3 = predict(Model3, type = "response")
predictTrain4 = predict(Model4, type = "response")

AllTrainPredictions = c(predictTrain1, predictTrain2, predictTrain3, predictTrain4)
AllTrainOutcomes = c(Train1$went_on_backorder, Train2$went_on_backorder, Train3$went_on_backorder, Train4$went_on_backorder)

```

ROC
```{r}
ROCRpred = prediction(AllTrainPredictions, AllTrainOutcomes)
ROCRperf = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf)

ROCRauc = performance(ROCRpred, "auc")
ROCRauc@y.values 
```

OUT OF SAMPLE TESTING
```{r}
# Convert to factor variables -- TEST SET 
test$potential_issue = as.factor(test$potential_issue)
test[18:22] = lapply(test[18:22], as.factor)
str(test)

Test1 = subset(test, clusterTest == 1)
Test2 = subset(test, clusterTest == 2)
Test3 = subset(test, clusterTest == 3)
Test4 = subset(test, clusterTest == 4)
```

```{r}
predictTest1 = predict(Model1, newdata = Test1, type = "response")
predictTest2 = predict(Model2, newdata = Test2, type = "response")
predictTest3 = predict(Model3, newdata = Test3, type = "response")
predictTest4 = predict(Model4, newdata = Test4, type = "response")
```

```{r}
AllTestPredictions = c(predictTest1, predictTest2, predictTest3, predictTest4)
TestSku = c(Test1$sku, Test2$sku, Test3$sku, Test4$sku)

predTest = data.frame(TestSku, AllTestPredictions)
str(predTest)
summary(predTest)
```

```{r}
colnames(predTest) = c("sku", "went_on_backorder")
str(predTest)
write.csv(predTest, "Submission1.csv", row.names = FALSE)
```


